### 2015-06-03 tex/th1.tex
2 jun

\begin{theo} \label{decisionptime}
The decision version of a function in $\E1$ is in \textsc{P}.
\end{theo}
\begin{proof}
Let $f$ be a function in $\E1$. Then there is a formula $\varphi(\x,\X,\z)$ such that
\begin{eqnarray*}
f(\A) &=& \mid \{ \langle\P,\e\rangle \mid \A \models \exists \x \, \varphi(\x,\P,\e) \} \mid,
\end{eqnarray*}
where $\A = \langle A, \S^{\A}, \leq^{\A} \rangle \in \Truc$, $\z$ is an $m$-tuple of variables and $\x$ is a $k$-tuple of variables. Let $n = \vert A \vert^m$ and $\e_1,\dots,\e_n \in A^m$ be all possible assignments for $\z$. Let $\ell = \vert A \vert^k$ and $\d_1,\dots,\d_\ell\in A^k$ be all possible assignments for $\x$. Note that $m$ and $k$ are fixed values, so both $\ell = \vert A \vert^k$ and $n=\vert A \vert^m$ are polynomial in the size of $\A$. Let $\varphi_\A(\X)$ be defined as follows:
\begin{eqnarray*}
\varphi_\A(\X) = \varphi(\d_1,\X,\e_1) \vee \cdots \vee \varphi(\d_1,\X,\e_n) \vee \varphi(\d_2,\X,\e_1) \vee \cdots \vee \varphi(\d_n,\X,\e_n).
\end{eqnarray*}
Note that $\varphi_\A(\X)$ will have at least one assignment $\P$ for $\X$ such that $\A\models\varphi_\A(\P)$ iff $f(\A)>0$. Let $\psi_\A(\X)$ be the formula that results of changing every satisfied sub-formula for a tautology and every non-satisfied sub-formula for a contradiction. We can do this since checking $\A\models\varphi(\d_i,\X,\e_i)$ can be done in polynomial time for each $i\in\{1,\ldots,n\}$. Note as well that $\varphi_\A(\X)$ is quantifier-free and its size is polynomial to the size of $\varphi(\x,\X,\z)$. Then, let $f'$ be defined as follows:
\begin{eqnarray*}
f'(\A) &=& \mid \{ \langle\P\rangle \mid \A \models \psi_\A(\P) \} \mid.
\end{eqnarray*}
Clearly $f' \in\#\Sigma_0$. Also, note that for every $\A$, $f(\A) > 0$ iff $f'(\A) > 0$, so computing $f'$ is enough to solve the decision version of $f$. However, it is showed in \cite{DBLP:journals/jcss/SalujaST95} that any counting problem in $\#\Sigma_0$ is computable in polynomial time. Therefore, the decision version of $f$ is in {\sc P}.
\end{proof}

>>>>

%!TEX root = sharp-sigma-one-plus.tex
\begin{theo} \label{decisionptime}
The decision problem associated to a function in $\E1$ is in \textsc{P}.
\end{theo}
\begin{proof}
Let $f$ be a function in $\E1$. Then there is an extended quantifier-free $\L-$formula $\varphi(\x,\X,\z)$ such that
\begin{eqnarray*}
f(\A) &=& \mid \{ \langle\P,\e\rangle \mid \A \models \exists \x \, \varphi(\x,\P,\e) \} \mid,
\end{eqnarray*}
where $\A = \langle A, \S^{\A}, \leq^{\A} \rangle \in \Truc$, $A = \{a_1,\ldots,a_{\vert A \vert}\}$, $\z$ is an $m$-tuple of variables and $\x$ is a $k$-tuple of variables. As said in \cite{DBLP:journals/jcss/SalujaST95}, a function $h:\Truc \to \N$ is in $\#\Sigma_0$ if there exists a quantifier-free $\L$-formula $\theta(\Y,\y)$ such that $h = f_{\theta(\Y,\y)}$. Let $\y = (\x,\z)$ and let $\psi(\X,\y) = \varphi(\x,\X,\z)$. Moreover, let $g = f_{\psi(\X,\y)}$.
\begin{claim}
For each $\A \in \Truc$, $f(\A) > 0$ iff $g(\A) > 0$.
\end{claim}
\begin{proof}
($\Rightarrow$) Suppose $f(\A) > 0$. Let $\P$ and $\e$ be such that $\A \models \exists \x \, \varphi(\x,\P,\e)$. It follows that there is at least one $\d \in A^k$ such that $\A \models \varphi(\d,\P,\e) = \psi(\P,(\d,\e))$. Therefore, $g(\A) > 0$. ($\Leftarrow$) Suppose $g(\A) > 0$. Let $\Q$ and $\c = (\c_1,\c_2)$, where $\c_1$ and $\c_2$ have $k$ and $m$ elements respectively, be such that $\A \models \psi(\Q,\c) = \varphi(\c_1,\Q,\c_2)$. Therefore, $\A \models \exists \x \, \varphi(\x,\Q,\c_2)$, from which we conclude that $f(\A) > 0$.
\end{proof}
Clearly $g \in\#\Sigma_0$. As we showed, computing $g$ is enough to solve the decision version of $f$. Therefore, given that any counting problem in $\#\Sigma_0$ is computable in polynomial time \cite{DBLP:journals/jcss/SalujaST95}, we conclude that the decision version of $f$ is in {\sc P}.
\end{proof}
